---
title: "Rd_HowTo"
author: "BilalsGituation"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages("billboard")
library(tidyverse)
library(billboard)
library(usethis)
```

## R Documentation

A reference guide for creating .Rd files by @BilalsGituation, 
as reaccessing info is easier when it's text than a video

Info from here https://www.youtube.com/watch?v=gl9fFmtXFcI

I really hope I am not stepping on anyone's toes by naming this package
"Bilalboard100Tutorial". It seems very unlikely, but I apologise if I am.

## Setup

start by opening a new project "R Package using devtools"

use_package() will allow the developer to use other scripts as jumping-off points for packages that should ultimately have different functions


```{r Retrieve Template Package, echo=TRUE}
use_package("billboard")
```


use_r("function_name") will create an empty script in your directory for you to copy the function to edit into (see files of this repo)


```{r Create file for your function, echo=TRUE}
use_r("random_tune")
```

## Adding functions

As we don't have an aim other than learning how to produce documented R packages, we use the template random_song() function from the "billboard" package

tip for the youtube uploader: I should be able to copy the functions from your git page, but one isn't provided

```{r Copied Template Functions, echo=TRUE}
data("wiki_hot_100s")
songs <- wiki_hot_100s %>%
  mutate(no = case_when(
    no == "Tie" ~ lag(no),
    T ~ no
  )
  ) %>%
  mutate(score = 1+1/as.numeric(no))


tunes <- songs %>%
  group_by(title, artist) %>%
  summarise(score = sum(score),
            n_years = n(),
            .groups = "drop") # I don't really know what these do,
# but I think I will need them for random_tune below

artists <- tunes %>%
  group_by(artist) %>%
  summarise(score = sum(score),
            n = sum(n_years),
            .groups = "drop")

# This is what you copy into your empty script file. I haven't got the Rmd
# file to do that
#######################THE##FUNCTION############################################

random_tune <- function(artist = "Amerie", data = billboard::wiki_hot_100s){
  data <- data[data$artist == artist,]
  song <- base::sample(data$title, 1)
  cat(paste0("Random song by ",artist," : ", song))
} # Default arguments will get the user a huge banger, as opposed to the suggested default of Rihanna. 
#Sorry mate. 

```

```{Store the function in the package, rather than the env}
#This function will load the functions from the 
devtools::load_all(".")
#Which makes this work in the console once a function is copied in
random_tune()
random_tune(artist = "Ray Charles")
```

## Documenting your function

In RStudio,
Roxygen2 skeleton is produced using Ctrl+Shift+Alt+R, when the cursor is inside
the definition of an R function. It starts like this:

```{r Roxygen, echo=TRUE}
#' Title
#'
#' @param artist 
#' @param data 
#'
#' @return
#' @export
#'
#' @examples
random_tune <- function(artist = "Amerie", data = billboard::wiki_hot_100s){
  data <- data[data$artist == artist,]
  song <- base::sample(data$title, 1)
  cat(paste0("Random song by ",artist," : ", song))
}
```

```{r Roxygen2, echo=TRUE}
#' Randomly select a tune (default: by Amerie, from the wiki_hot_100s)
#'
#'
#' @param artist An artist/group to select a song from (default=Amerie)
#' @param data The dataset to use (default= billboard::wiki_hot_100s)
#' 
#'
#' @return A random song is printed to the console
#' @export
#'
#' @examples random_tune()
#' @examples random_tune(artist = "Ray Charles")
#' 
random_tune <- function(artist = "Amerie", data = billboard::wiki_hot_100s){
  data <- data[data$artist == artist,]
  song <- base::sample(data$title, 1)
  cat(paste0("Random song by ",artist," : ", song))
}

# save this and then go to your build tab in RStudio and select "Document"
```

## man folder

We have successfully written a .Rd file using the Roxygen2 workflow, random_tune.Rd
My build tab gave the following output, commented out so it isn't executed:
```{Build tab input/output}
# ==> devtools::document(roclets = c('rd', 'collate', 'namespace'))
# 
# ℹ Updating Bilalboard100Tutorial documentation
# ℹ Loading Bilalboard100Tutorial
# Warning: [random_tune.R:7] @return requires a value
# Writing 'random_tune.Rd'
# Writing 'NAMESPACE'
# Documentation completed
```

```{r Check our help file}
rm(list = c("random_tune"))
devtools::load_all(".")
?random_tune
```

Our help file is there!

you can test out how well you made the examples section by choosing "Clean and
Install" in the build tab. This will load your library anew, then the following
code should work:

```{r Run your Examples, echo =TRUE}
# This is what you should see in your "Build" window, to show that you've updated the
# package in your library
#==> Rcmd.exe INSTALL --preclean --no-multiarch --with-keep.source Bilalboard100Tutorial
example(random_tune, package = "Bilalboard100Tutorial")
```

I am not going to upload this to CRAN, I'll learn that when I have something
original to put up there. Please comment if I have missed anything out, written
anything ambiguous or wrong, or anything like that.
